\textbf{CMCS 818J Project Final Report} \\ Implementing Streaming Authenticated Data Structures

### 2012-12-20 doc/final_report/draft_report.tex
Edits Section 2

	A verifiable computation (VC) is one in which computation can be performed on behalf of a requester, or client, by an untrusted resource but can be verified to be correct by the client.
	In this scenario, the client usually cannot, or wishes not to, perform the entire computation themselves and thus needs a way to verify the computation efficiently. 
	The growth of outsourced computation in the form of cloud computing has attracted a strong interest in the VC problem, and a considerable amount of research has been devoted to these problems \cite{evsc}.

	The Streaming Authenticated Data Structure scheme (SADS) does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
		\item Independence of prover (server) and verifier(client) : the prover and the verifier update their internal state without interaction.
		\item Efficiency : It can be shown that an exponential improvement for many commonly queries in the prover's running time can be achieved.
		\item Expressiveness : a wide range of queries such as membership/ non-membership, successor, range search and frequencies can be supported using this scheme.
	\end{enumerate} 
	The ultimate goal of the proposed scheme is to implement the SADS scheme that enable the verification of computation performed by an untrusted resource.

	The rest of this paper is organized as follows. We will be describing streaming authenticated data structure goals.
	Some recent research in streaming verifiable computation will be discussed.
	We then describe the homomorphic property used in the the SADS scheme. Some definitions will be presented in the following section.
	We present significant features of our implementation afterwards followed by presenting the performance of our investigation.
	Finally, we conclude our paper by providing some future plans.

\section{ Achieving independence through \\ a Lattice-based Hash Tree }

@@

\section{ Participants }

@@

\section{ Implementation }

@@

\section{Looking Forward}

	\subsection{ Production Quality Libraries }

@@

\begin{thebibliography}{9}
	\bibitem{sads} Elaine Shi, Charalampos Papamanthou \emph{Streaming Authenticated Data Structures}, Date Unknown
	\bibitem{evsc} B. Applebaum, Y. Ishai and E. Kushilevitz \emph{From Secrecy to Soundness: Efficient Verification via Secure Computation}
	\end{thebibliography}

>>>>

	A verifiable computation (VC) is one in which computation can be performed by a server on behalf of a client where the server is an untrusted resource.
	In this scenario, the client usually cannot, or wishes not to, perform the entire computation themselves but requires a means of verifying the computation efficiently.
	The growth of outsourced computation in the form of cloud computing has attracted a strong interest in the VC problem.
	In the streaming setting, many solutions to this problem have been proposed but so far have required inefficient protocols requiring the client and server to communicate updates as each stream element arrives.
	This communication requirement is prohibitively expensive in certain streaming applications where elements arrive in rapid succession, or are continuous.

	The Streaming Authenticated Data Structure scheme (SADS) \cite{dads} does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
		\item Independence of prover (server) and verifier (client) : the prover and the verifier can update internal state without interaction.
		\item Efficiency : SADS demonstrates an exponential improvement in server's running time for many common query types.
		\item Expressiveness : a wide range of queries such as (non-)membership, successor, range search and frequencies can be supported
	\end{enumerate} 
	The ultimate goal of the proposed scheme is to implement the SADS scheme that enable the verification of computation performed by an untrusted resource.

	The rest of this paper is organized as follows. 
	Section \ref{sec:tree} will discuss the key data structure use to achieve the SADS goals.
	Section \ref{sec:parts} will discuss the key components in the SADS scheme.
	Section \ref{sec:impl} will discuss details of our implementation \ref{sec:forward} will discuss preliminary measurements and future improvements.

\section{ Achieving Independence through \\ a Lattice-based Hash Tree }
\label{sec:tree}

@@

\section{ Participants }
\label{sec:parts}

@@

\section{ Implementation }
\label{sec:impl}

@@

\section{Looking Forward}
\label{sec:forward}
	\subsection{ Production Quality Libraries }

@@

\begin{thebibliography}{9}
	\bibitem{sads} Elaine Shi, Charalampos Papamanthou \emph{Streaming Authenticated Data Structures}, Date Unknown
%	\bibitem{evsc} B. Applebaum, Y. Ishai and E. Kushilevitz \emph{From Secrecy to Soundness: Efficient Verification via Secure Computation}
	\end{thebibliography}
